On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-17 anthropomorphism.tex
Added figure on cognitive phases

\caption{Dynamics of anthropomorphism. We distinguish three main phases:
\emph{initialization}, \emph{familiarization} and \emph{stabilization}. In the
pre-interaction phase, users build an \emph{initial capital of
anthropomorphism} (ICA). Once the interaction starts, the level of
anthropomorphism increases due to the \emph{novelty effect}, and then decreases
to reach a \emph{stabilized level of anthropomorphism} (SLA).
During the interaction, unpredicted behaviors of the robot (\emph{disruptive
behaviors}) locally increase the level of anthropomorphism.}
\label{fig|dynamics}
\end{figure*}

@@

>>>>

\caption{Dynamics of anthropomorphism. We distinguish three main phases:
\emph{initialization}, \emph{familiarization} and \emph{stabilization}. In the
pre-interaction phase, users build an \emph{initial capital of
anthropomorphism} (ICA). Once the interaction starts, the level of
anthropomorphism increases due to the \emph{novelty effect}, and then decreases
to reach a \emph{stabilized level of anthropomorphism} (SLA).
During the interaction, unpredicted behaviors of the robot (\emph{disruptive
behaviors}) locally increase the level of anthropomorphism.}
\label{fig:dynamics}
\end{figure*}

@@

\subsection{Anthropomorphism and Cognitive Models}
\label{sec:cognitivemodel}

\begin{figure}[htb]
\centering
%\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8, transform shape]
\baselineskip=8pt

% horizontal axis
\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
% labels
\draw   (2,0) node[anchor=north] {Phase I}
        (5,0) node[anchor=north] {Phase II}
        (8,0) node[anchor=north] {Phase III};

\draw[dotted] (3.5, -0.5) -- (3.5,6);
\draw[dotted] (6.5, -0.5) -- (6.5,6);

% vertical axis
\draw[-|] (0,0) -- (0,6) node[anchor=east] {};
% Us
\draw[thick] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) -- (10,6);

\draw (2.2,2) node[align=center] {\scriptsize{sub-cognitive}\\\scriptsize{anthropomorphism}}; %label
\draw (5,3.85) node[align=center] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
\draw (8.5,5.85) node[align=center] {\scriptsize{adapted mental model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (antropomorphic or not)}}; %label

\draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behaviour) \\ \tiny \it or short interaction}; %label
\draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label

\end{tikzpicture}
%}
\caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
sub-cognitive identification of living peers. {\it Empathy} [TO DISCUSS] is characteristic
of this stage. After longer observation or short, uncontextualized interaction
(typically, a lab environment), the user enters Phase II: the user projects a
mental model he/she is already familiar with onto the robot. This leads to
expectation regarding the cognitive abilities of the robot. After longer {\it
contextualized} interaction (typically, at home), the user enters Phase III of
anthropomorphism: the user recomposes an accurate mental model of the robot,
based on experience. This leads to adapted interaction modalities, that may
still be anthropomorphic, or not.}
\label{fig:cognitivemodel}
\end{figure}

Figure~\ref{fig:cognitivemodel} offers a cognitive perspective on the dynamics
of anthropomorphism presented in the previous section.
